Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-03-07 article-models-ttmodels.tex
reorganizing compatibility rules

\subsection{Compatibility properties of arbitrary terms}

@@

>>>>

\subsection{Compatibility properties of arbitrary terms}
In this subsection we will state the inference rules that assert that every
term $\jterm{{\Gamma}{A}}{P}{f}$ acts functorially. That means, every term
preserves the empty context, extension, weakening, substitution and the
identity functions. Moreover, there will be several inference rules
involving the behavior of $\mfam{f}$ and $\mtm{f}$.

@@

\subsubsection{The action of the action on families of a term is the action
on contexts of that term}
Consider a term $\jterm{{\Gamma}{A}}{P}{f}$. Then we have the term
\begin{equation*}
\jterm
  {{\Gamma}{\subst{\tfemp{A}}{\mfam{A}}}}
  {\subst{\tfemp{A}}{\ctxwk{\mfam{A}}{\subst{f}{\mfam{P}}}}}
  {\subst{\tfemp{A}}{\mfam{f}}}
\end{equation*}
We have required that $\subst{\tfemp{A}}{\mfam{A}}\jdeq A$. Also, we have the
judgmental equalities
\begin{align*}
\subst{\tfemp{A}}{\ctxwk{\mfam{A}}{\subst{f}{\mfam{P}}}}
& \jdeq
  \ctxwk{\subst{\tfemp{A}}{\mfam{A}}}{\subst{\tfemp{A}}{{f}{\mfam{P}}}}
  \\
& \jdeq
  \ctxwk{A}{\subst{{\tfemp{A}}{f}}{{\tfemp{A}}{\mfam{P}}}}
  \\
& \jdeq
  \ctxwk{A}{\subst{\tfemp{\subst{\tfemp{A}}{P}}}{{\tfemp{A}}{\mfam{P}}}}
  \\
& \jdeq
  \ctxwk{A}{\subst{{\tfemp{A}}{\tfemp{P}}}{{\tfemp{A}}{\mfam{P}}}}
  \\
& \jdeq
  \ctxwk{A}{\subst{\tfemp{A}}{{\tfemp{P}}{\mfam{P}}}}
  \\
& \jdeq
  \ctxwk{A}{\subst{\tfemp{A}}{P}}
\end{align*}
If we require also the following inference rule, we would get $\mfam{A}\jdeq
\ctxwk{A}{A}$.
\begin{equation*}
\inference
  { \jfam{{\Gamma}{A}}{P}
    }
  { \jfameq{{\Gamma}{A}}{P}{\ctxwk{A}{\subst{\tfemp{A}}{P}}}
    }
\end{equation*}
This rule would say that a family $P$ of models over $A$ is determined by the
model $\subst{\tfemp{A}}{P}$ and that the only possible families of models
are the constant families.
